surfing

### 2021-06-30 inst/surfing.Rmd
name chunks
whitespace

```{r}
plot(c(0,p),c(l0,l)-max(l),type='b',xlab="Brazilian beachtype",ylab="support")
```

@@

```{r}
plot(c(0,p_wide),c(l0,l_wide)-max(l),type='b',xlab="Brazilian beachtype",ylab="support")
```

@@

```{r}
all_Brazilian_surfers <- rownames(surfing_table)[surfing_table$nation == "BRA"]
all_Brazilian_surfers
pnames(surfing2)
pnames(surfing2) %in% all_Brazilian_surfers
table(pnames(surfing2) %in% all_Brazilian_surfers)
Brazilian_surfers <- pnames(surfing2)[pnames(surfing2) %in% all_Brazilian_surfers]
Brazilian_surfers
```

```{r,cache=TRUE}
f <- function(B,...){
  jj <- specificp.test(surfing2, "Brazilian_beachtype", B)
  mp <- jj$null_estimate
  n <- sum(names(mp) %in% all_Brazilian_surfers)
  GLO <- log(mp["Brazilian_beachtype"]^n/prod(mp[which(names(mp) %in% all_Brazilian_surfers)]))
  out <- c(B,GLO, support=jj$null_support)
  names(out) <- c("B","GLO","support")
  return(out)
}
```

@@

```{r}
plot(M[,2],M[,3]-max(M[,3]),type='b',xlab="Brazilian beachtype (log-odds)",ylab="support")
plot(M[,2],M[,3]-max(M[,3]),type='b',ylim=c(-0.3,0),xlab="Brazilian beachtype (log-odds)",ylab="support")
```

@@

```{r}
pie(maxs)
```

@@

```{r}  
plot(p,l,type='b',xlab="compatriot support",ylab="support")
```

```{r}
scomp3
maxp(scomp3)
specificp.gt.test(scomp3,'S',0)
````

>>>>

```{r plotpthink}
plot(c(0,p),c(l0,l)-max(l),type='b',xlab="Brazilian beachtype",ylab="support")
```

@@

```{r plotwidep}
plot(c(0,p_wide),c(l0,l_wide)-max(l),type='b',xlab="Brazilian beachtype",ylab="support")
```

@@

```{r allbrazsurf}
all_Brazilian_surfers <- rownames(surfing_table)[surfing_table$nation == "BRA"]
all_Brazilian_surfers
pnames(surfing2)
pnames(surfing2) %in% all_Brazilian_surfers
table(pnames(surfing2) %in% all_Brazilian_surfers)
Brazilian_surfers <- pnames(surfing2)[pnames(surfing2) %in% all_Brazilian_surfers]
Brazilian_surfers
```

```{r biglikefun,cache=TRUE}
f <- function(B,...){
  jj <- specificp.test(surfing2, "Brazilian_beachtype", B)
  mp <- jj$null_estimate
  n <- sum(names(mp) %in% all_Brazilian_surfers)
  GLO <- log(mp["Brazilian_beachtype"]^n/prod(mp[which(names(mp) %in% all_Brazilian_surfers)]))
  out <- c(B,GLO, support=jj$null_support)
  names(out) <- c("B","GLO","support")
  return(out)
}
```

@@

```{r plotBraz}
plot(M[,2],M[,3]-max(M[,3]),type='b',xlab="Brazilian beachtype (log-odds)",ylab="support")
plot(M[,2],M[,3]-max(M[,3]),type='b',ylim=c(-0.3,0),xlab="Brazilian beachtype (log-odds)",ylab="support")
```

@@

```{r plotpiemaxs}
pie(maxs)
```

@@

```{r plotprofilescomp}  
plot(p,l,type='b',xlab="compatriot support",ylab="support",main="profile support for S, scomp")
```

```{r scomp3maxp, cache=TRUE}
scomp3
maxp(scomp3)
specificp.gt.test(scomp3,'S',0,n=100)
````

```{r profsuppcalcscomp3atriotmonster, cache=TRUE}
p <- c(0.0002,seq(from=0.001,to=0.02,len=10))
l <- profsupp(scomp3,"S",p,relative=FALSE,n=100)
```

```{r plotprofilescomp3}  
plot(p,l,type='b',xlab="compatriot support",ylab="support",main="profile support for S, scomp3")
```
